Tight Generalization Bounds for Hard Parameter Sharing in High-dimensional Linear Regression

### 2020-10-12 arxiv/setup.tex

There are two main ideas in our analysis. The proof of our first result uses a geometric intuition that hard parameter sharing finds a ``rank-$r$'' approximation of the datasets.
We carefully keep track of the concentration error between the global minimum of $f(A, B)$ and their population version.
The proof of our second result is significantly more involved because of different sample sizes and covariate shifts.
\HZ{add several sentences on the technical insight}
One limitation of our analysis is that for two tasks with different sample sizes, there is extra error term in the prediction loss of hard parameter sharing (cf. equation \eqref{cor_MTL_error}), which can be large for very small $n_1$. This involves a study of the asymptotic singular values distribution of a non-symmetric random matrix plus an identity matrix, which is still an open problem in random matrix theory due to lack of freeness. 
%\HZ{add why this is challenging}

>>>>

There are two main ideas in our analysis. The proof of our first result uses a geometric intuition that hard parameter sharing finds a ``rank-$r$'' approximation of the datasets.
We carefully keep track of the concentration error between the global minimum of $f(A, B)$ and their population version.
The proof of our second result is significantly more involved because of different sample sizes and covariate shifts. We use some modern random matrix theory techniques developed in the past decade to obtain the sharp generalization bound \cite{erdos2017dynamical}. In particular, we use the novel technique in \cite{Anisotropic} to obtain a sharp estimate on the inverse of the sum of two sample covariance matrices with arbitrary population covariance matrices, which is commonly referred to as the \emph{local law}. 
%\HZ{add several sentences on the technical insight} 
One limitation of our analysis is that for two tasks with different sample sizes, there is extra error term in the prediction loss of hard parameter sharing (cf. equation \eqref{cor_MTL_error}), which can be large for very small $n_1$. This involves a study of the asymptotic singular values distribution of a non-symmetric random matrix plus an identity matrix, which is still an open problem in random matrix theory due to lack of freeness. 
%\HZ{add why this is challenging}
